---
title: "Correlation between mutual fund and index"
author: "Yeung Ka Ming, CFA"
date: "`r Sys.Date()`"
output:
  md_document:
    variant: gfm
    preserve_yaml: TRUE
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../_posts") })
excerpt: "Correlation"
layout: post
tags: correlation regression
---
  
```{r set-options, echo=FALSE, cache=FALSE}
options(width = 100)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, error = FALSE, message = FALSE, fig.width = 10)
```

# Summary
To see how the selected mutual fund performed verse a major China A-share market index.

Mutual fund
- AMUNDI INTERINVEST CHINA A SHARES[^1]

China A-share market index
- CSI300[^2]

- The mutual fund return is negatively correlated to CSI300. 
**One of the reasons might be due to 2015 Chinese Yuan devaluation.**

- Regression shows that CSI300 cannot explain the performance of the fund. 
**The fund is very likely employing active management.**

## R Libraries
```{r}
library("quantmod")
library("tidyverse")
library("tidyquant")
library("PerformanceAnalytics")
```

## Preparation of data
Data is directly downloaded from web, which is publicly available:
```{r Setup environment, include=FALSE, cache=FALSE}
set.seed(1234)
setwd("C:/Users/USER/OneDrive - The Chinese University of Hong Kong/Github-Pages/iyeung144.github.io/_source")
base_dir <- "C:/Users/USER/OneDrive - The Chinese University of Hong Kong/Github-Pages/iyeung144.github.io/" # i.e. where the jekyll blog is on the hard drive.
base_url <- "/" # keep as is
fig_path <- "images/" # customize to heart's content, I 'spose.

knitr::opts_knit$set(base.dir = base_dir, base.url = base_url)
knitr::opts_chunk$set(fig.path = fig_path,
                      cache.path = '../cache/',
                      message=FALSE, warning=FALSE,
                      cache = TRUE) 
```

```{r import data}
data_csi300_tbl <- read_csv("CSI300.csv", col_types = "Dd")
data_amundi_tbl <- read_csv("amundi.csv", col_types = "Dd")
```

Daily log returns of the fund and the index are calculated:
```{r return}
data_csi300_tbl <- data_csi300_tbl %>% mutate(csi300_return = log(CSI300_Close) - log(lag(CSI300_Close)))
data_amundi_tbl <- data_amundi_tbl %>% mutate(amundi_return = log(amundi) - log(lag(amundi)))
```

Combine two tibbles by **left_join**:
```{r join data by date}
data1 <- data_csi300_tbl %>% left_join(data_amundi_tbl, by =c("Date")) %>% drop_na()
```

## Correlation results
Correlation result is listed below:
```{r correlation}
amundi_csi300 <- cor(data1$csi300_return, data1$amundi_return)

knitr::kable(c(Amundi = amundi_csi300), 
             col.names = "Amundi correlation w/ CSI300")
```

Interesting, the fund is negatively correlated with CSI300. The cumulative return of the fund and index are:
```{r}
csi300_ret <- tail(data1$CSI300_Close,1) / head(data1$CSI300_Close,1)
amundi_ret <- tail(data1$amundi,1) / head(data1$amundi,1)

knitr::kable(c(CSI300 = csi300_ret, Amundi = amundi_ret), 
             col.names = "Cumulative return")
```

One of the reasons can be attributed to 2015 Chinese Yuan devaluation. We can also see that from Amundi chart in the website, the performace between the fund and the index diverages starting from 2015.

## Regression with CSI300
Daily return regression between the fund and the index is analysed below:
```{r lm}
reg1 <- lm(amundi_return ~ csi300_return, data1)
```

We can tell from the regression result that CSI300 actually cannot explain the return of the fund, so the portfolio manager is very like employing active management.
```{r regression result}
summary(reg1)
plot(data1$csi300_return, data1$amundi_return, pch=".", xlab = "CSI300 daily return", ylab = "Amundi daily return")
abline(lm(data1$csi300_return ~ data1$csi300_return), col='red', lwd=1)
```

## Reference
[^1]: https://www.amundi.lu/retail/product/view/LU0832972474
[^2]: http://www.csindex.com.cn/en/indices/index-detail/000300